Dynamics of Laterally Propagating Flames in X-ray Bursts. II. Realistic Burning \& Rotation

### 2021-01-26 xrb2/paper.tex
Removed margin comment

We investigate the effect of rotation rate on the flame. With the
exception of IGR J17480-2446 (\citealt{altamirano2010discovery}, spinning at $11~\mathrm{Hz}$), most observations of
XRBs come from sources with rotation rates of $200-600~\mathrm{Hz}$
\citep{bilous:2019,galloway:2020}. There are a number of
factors that could explain this lack of observations below $200~\mathrm{Hz}$. It
could be that there is some physical process which inhibits the flame
ignition and/or spread at lower rotation rates. It could be that burst
oscillations at lower rotation rates are smaller in amplitude and
therefore more difficult to detect. It could be that it does not have
anything to do with the flame at all, but that neutron stars in
accreting low mass X-ray binaries rarely have rotation rates below $200~\mathrm{Hz}$ 
\MarginPar{look into this?}.

>>>>

We investigate the effect of rotation rate on the flame. With the
exception of IGR J17480-2446 (\citealt{altamirano2010discovery}, spinning at $11~\mathrm{Hz}$), most observations of
XRBs come from sources with rotation rates of $200-600~\mathrm{Hz}$
\citep{bilous:2019,galloway:2020}. There are a number of
factors that could explain this lack of observations below $200~\mathrm{Hz}$. It
could be that there is some physical process which inhibits the flame
ignition and/or spread at lower rotation rates. It could be that burst
oscillations at lower rotation rates are smaller in amplitude and
therefore more difficult to detect. It could be that it does not have
anything to do with the flame at all, but that neutron stars in
accreting low mass X-ray binaries rarely have rotation rates below $200~\mathrm{Hz}$.
